\documentclass[11pt]{article}
\usepackage[margin=1.2cm]{geometry}
\usepackage{enumitem}% http://ctan.org/pkg/enumitem
\usepackage{titlesec}

\titleformat{\section}
  {\normalfont\Large\bfseries}{\thesection}{1em}{}[{\titlerule[.8pt]}]


\begin{document}

\pagestyle{empty}

\begingroup  
  \centering
  \LARGE {\bf Adam Keim}\\
a\_keim@coloradocollege.edu | https://github.com/adam-keim \\

%\noindent\hrulefill
\endgroup



\section*{Education:}

{\bf Currently Enrolled: Bachelor of Arts,} Physics, Chemistry ({\bf GPA: } 3.87) \hfill May 2024\\
Colorado College, Colorado Springs, CO. \\
{\bf Concentration:} Comprehensive Physics. \\
{\bf Relevant Coursework Taken:} Quantum II, Optics,  Solid State Physics, Techniques of Experimental Physics, Instrumental Chemistry, Organic Chemistry II, Electronics I, Computational Graph Theory, Physical Chemistry I, Computational Physics.  \\
{\bf Planned Coursework Spring 2023:} Electromagnetism, Thermal Physics

\section*{Honors and Awards:}
{\bf Colorado College} Dean's List '20-'21, '21-'22, '22-'23. \\ 
{\bf Colorado College} First Year Chemistry Award '20-'21. \\
{\bf American Chemical Society} Undergraduate Award in Physical Chemistry '22-'23.\\
{\bf Colorado College} Student Seed and Innovation Grant: Modular Synthesis - An Exploration of the Natural World through Sound. Awarded Jan. 2023.

\section*{Presentations:}

{\bf Colorado College} Molecular Crystallization in the Electrical Double Layer -- Poster Presentation Feb. 2022
{\bf NIST} Cryogenic Low-Noise DC Measurements of Nanoscale Josephson Junctions -- Colloquium Presentation Aug. 2023


\section*{Skills and Languages:}
{\bf Computer Languages: }{\em Python, Java, C++}, C, Rust, Go, JavaScript.\\
{\bf Software:} {\em Linux SysAdmin, Git, KiCad, Fusion360, VISA}, AWS, Bash, CI/CD, Test-Driven Development, Docker, Infrastructure-as-Code, \LaTeX.\\
{\bf Embedded Skills:} {\em Arduino, ESP-32}, STM32, Cross-Platform Unit Testing, Displays.\\
{\bf Electronics:} Analog signal amplification, digitization, and processing, Digital protocols, SMD Soldering, Oscilloscope, SPICE. \\
{\bf Lab:} Organic Synthesis, Cryogen Handling, Data Analysis.\\
{\bf Fabrication:} {\em 3D Printing}, CNC, Laser Cutting, Machining (Lathe, Mill), Woodworking. \\

\noindent\textbf{\underline{Languages:}} \\
\textbf{English}: Native speaker, reader, and writer. \\
\textbf{French}: Native speaker \& reader, proficient writer.

\section*{Experience:}

\noindent
{\bf Student Researcher (SURF)} \hfill May. 2023 --- Aug. 2023 \\
{\sl Flux Quantum Electronics Project, Superconductive Electronics Group} National Institute of Standards and Technology, Boulder, CO.
\begin{itemize}[topsep=0pt] \itemsep -4pt
	\item Designed, assembled, and integrated PCBs to assist with characterization of nanoscale Josephson Junctions (JJ's)
	\item Characterized superconducting JJ's voltage/current characteristics at liquid helium temperatures, using Python for automation of acquisition and analysis.
	\item Modeled JJ's numerically using a variety of approaches, and fit these models to experimental data.
	\item Addressed signal integrity issues (ground loops, interference, trapped flux) in order to realize measurements with nA precision.
	\item Presented my research at the SURF Colloquium at the end of the summer to other students and NIST staff.
\end{itemize}
%\bigskip

\noindent
{\bf Student Researcher} \hfill Oct. 2022 --- Nov. 2022 \\
{\sl Bowman Lab: Spin Crossover in Inorganic Cobalt Compounds} Colorado College, Colorado Springs, CO.
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Synthesized and characterized an inorganic cobalt-containing compound in an attempt to characterize its spin crossover properties.
\item Used ORCA to perform computational chemistry calculations to predict structure and vibrational spectra of the target compound. 
\item Used analytical and spectroscopic techniques including IR, NMR, Raman, and TGA with electromagnet to characterize the compound.
\end{itemize}
%\bigskip

\noindent
{\bf Student Researcher} \hfill Jun. 2022 --- Aug. 2022 \\
{\sl Light Lab: High-Voltage Nanosecond Pulse Generation} Colorado College, Colorado Springs, CO.
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Developed and constructed a high voltage nanosecond-scale pulse generator to be used in generation of low-temperature plasmas, based on a Marx generator topology.
\item Designed schematics and printed circuit boards of the design using KiCad.  Design features include a microcontroller for controls, optical triggering of individual stages, SiC MOSFETs, and numerous high-voltage signal paths.
\item Assembled, troubleshooted, and tested individual stages of the generator using oscilloscopes and signal generators to confirm that the output pulse met requirements. 
\end{itemize}
%\bigskip

\noindent
{\bf Student Researcher} \hfill Jun. 2021 --- Aug. 2021 \\
{\sl Fahrenkrug Lab: Molecular Crystallization within the Electrical Double Layer.} Colorado College, Colorado Springs, CO.
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Directed continued research in crystallization at the molecular double-layer under the influence of large electric fields.
\item Iterated on and fabricated electrochemical cells used for crystal growth.
\item Used electrochemical and spectroscopic techniques such as EIS, XRD, and chronocoulometry to characterize crystals. 
\end{itemize}
%\bigskip


\noindent{\bf Associate DevOps Engineer} \hfill Jun. 2019 --- Aug. 2020 \\
{\sl PowerReviews.} Chicago, IL
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Worked as part of a DevOps team architecting and maintaining software infrastructure.
\item Engineered a log processing application to aggregate customer data from API logs, built in Python utilizing AWS serverless functions and queue technologies.
\item Expanded and modernized server infrastructure by using Infrastructure-as-Code technologies to solve scaling and security issues.
\end{itemize}
%\bigskip

\noindent
{\bf DevOps Intern} \hfill Jun. 2018 --- Jun. 2019 \\
{\sl PowerReviews.} Chicago, IL
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Worked full-time for a summer, and part-time during the school year upgrading infrastructure and helping developers with IT issues. 
\item Designed Continuous Integration/Delivery pipelines to assist developers in shipping software.
\item Designed internal CLI tooling in Go to speed up connections to secure hosts.
\item Became familiar with concepts and tooling to make efficient use of AWS cloud technologies.
\end{itemize} 
%\bigskip

\noindent
{\bf QA Intern} \hfill Jun. 2017 --- Sep. 2017 \\
{\sl PowerReviews.} Chicago, IL
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Wrote automated unit and integration tests using JUnit for Java apps running in AWS. 
\end{itemize} 
%\bigskip

\noindent
{\bf Front-End Intern} \hfill Jun. 2015 --- Sep. 2015 / Jun. 2016 --- Sep. 2016\\
{\sl PowerReviews.} Chicago, IL
\begin{itemize}[topsep=0pt] \itemsep -4pt
\item Developed components for a client-facing ReactJS reviews webapp in Javascript over the course of two summers.
\end{itemize} 





\end{document}
